\section{Numerical diagnostics and finite certificates}
\label{sec:numerics}

No numerical statement in this section is used in
Theorem~\ref{thm:main}.  The analytic nonvanishing input comes from the exact
zero set \eqref{eq:L-zero-set} and Conrey's theorem, not from computed zeta
zeros.

\subsection{Implementation A: direct prime-power side}

The first implementation evaluates finite dyadic convolutions by an exact
nonuniform B-spline identity.  It enumerates every \(p^m\) in
\[
|2y-\log(p^m)|<1
\]
and records the triple \((p,m,p^m)\) and the exact coefficient
\((\log p)/\sqrt{p^m}\).  Packet truncations \(N=12,14,16\) are retained
separately.  An exact-rational computation certifies
\[
0.063637725597
<
\Ih(1/2)
<
0.088006928482.
\]
The finite window at \(y=1/2\) contains exactly
\[
2,\ 3,\ 4,\ 5,\ 7.
\]
The certificate includes the omitted infinite-convolution tail and does not
replace the infinite oscillation proof.

\subsection{Implementation B: independent Fourier and zero sides}

The second implementation computes \(K_h\) by Fourier inversion of the sinc
product on its direct side.  Independently, it evaluates the truncated
explicit formula through the product \eqref{eq:L-product} and zeta zeros.
At \(y=1.25,1.75,2.25\), the direct calculations retain respectively
\(15,26,50\) prime powers.  The two implementations agree to between
\(5.2\times10^{-13}\) and \(1.4\times10^{-11}\), inside their declared
diagnostic budgets.

At 220-bit Arb precision, selected coefficients at zero indices \(1,2,4\)
are certified to have strictly positive real intervals after enclosing the
infinite product tail.  The omitted nontrivial-zero sum is not certified;
therefore this computation makes no eventual-sign claim.

\begin{table}[ht]
\centering
\begin{tabular}{@{}rrr@{}}
\toprule
\(y\) & retained prime powers & \(|\Ih^{(A)}-\Ih^{(B)}|\)\\
\midrule
1.25 & 15 & \(5.13\times10^{-13}\)\\
1.75 & 26 & \(8.25\times10^{-12}\)\\
2.25 & 50 & \(1.32\times10^{-11}\)\\
\bottomrule
\end{tabular}
\caption{Cross-implementation diagnostics.}
\end{table}

Machine-readable JSON and CSV files in the repository contain every retained
prime power, including composite prime powers, rather than a primes-only
projection.
