\section{Logical scope and independent audit}

The analytic chain was reconstructed independently multiple times and
subjected to separate circularity audits.  The audited dependencies are:
\begin{itemize}[leftmargin=2em]
\item the frozen semilocal normalization
      \eqref{eq:preform};
\item elementary properties of the fixed infinite convolution;
\item absolute convergence of the Euler product in its initial half-plane;
\item standard meromorphic continuation and the functional equation of
      \(\zeta\);
\item the zero-counting estimate \(N_\zeta(T)=O(T\log T)\);
\item Conrey's unconditional positive-proportion theorem
      \cite{Conrey1989}; and
\item the Landau lemma proved in this paper.
\end{itemize}

The proof does not assume:
\begin{itemize}[leftmargin=2em]
\item the Riemann hypothesis;
\item global simplicity of zeta zeros;
\item linear independence of zero ordinates;
\item Weil positivity;
\item an eventual sign;
\item a numerical zero table;
\item convergence of a determinant;
\item completeness of any spectral realization; or
\item information about semilocal ground states.
\end{itemize}

The exact coefficient transform was fixed before any zero theorem was
applied.  Its invisible lattice was derived from the packet alone, so the
visible poles are not inserted by normalization.  The two numerical
implementations can be deleted without changing any step of the proof.

\begin{corollary}[Fixed-packet no eventual parity]
For the frozen packet,
\[
\Delta_h(y)\le0\quad\text{for all sufficiently large }y
\]
and
\[
\Delta_h(y)\ge0\quad\text{for all sufficiently large }y
\]
are both false.
\end{corollary}

This corollary is deliberately not a theorem about the parity of a true
ground state.  Such a statement would require uniform estimates over a
packet class and a variational comparison controlling the magnitude of the
interaction.  Neither is claimed here.
