\documentclass[11pt]{article}

\usepackage[a4paper,margin=30mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Z}{\mathbb Z}
\newcommand{\N}{\mathbb N}
\newcommand{\qform}{\mathfrak q}
\newcommand{\Ih}{\mathcal I_h}
\newcommand{\Lh}{L_h}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\Res}{\operatorname*{Res}}

\title{\textbf{Reflected-Packet Interactions in the Semilocal Weil Form}\\
\large An Exact Zero Expansion and Unconditional Infinite Oscillation}
\author{LeonardSEO}
\date{Version 1.0.0 --- 23 July 2026}

\begin{document}
\maketitle

\begin{abstract}
We freeze one explicit real, even, compactly supported smooth packet and
compute the interaction of two widely separated reflected translates in the
complete semilocal Weil preform.  The pole and all-prime-power sectors combine
into a Stieltjes pairing against \(d\psi-dx\).  Its canonical bilateral
Laplace transform is
\[
L_h(s)\left\{
\frac{\zeta'}{\zeta}\left(s+\frac12\right)
+\frac{1}{s-\frac12}
\right\}.
\]
A contour displacement gives an absolutely convergent expansion over all
nontrivial and trivial zeros.  The archimedean term and the remaining pole
term cancel the complete trivial-zero series, leaving a zero-only expansion
for the full reflected cross interaction.  The packet coefficient vanishes
exactly on the lattice \(4\pi i\Z\setminus\{0\}\).  Conrey's unconditional
positive-proportion theorem therefore supplies infinitely many visible
critical-line poles.  A Laplace-transform form of Landau's theorem then
excludes either eventual sign.  Consequently both the arithmetic interaction
and the even-minus-odd energy splitting take both strict signs arbitrarily
far out.
\end{abstract}

\begin{center}
\fbox{\begin{minipage}{0.91\textwidth}
\textbf{Scope.} This is not a proof of the Riemann hypothesis.  It is a
fixed-packet theorem.  It does not identify, approximate, or determine the
parity of an actual semilocal ground state.  Numerical computations in the
repository are diagnostics only and are not premises of the analytic proof.
\end{minipage}}
\end{center}

\tableofcontents

\input{sections/01_introduction}
\input{sections/02_frozen_specification}
\input{sections/03_prime_pole_interaction}
\input{sections/04_explicit_formula}
\input{sections/05_oscillation}
\input{sections/06_numerical_diagnostics}
\input{sections/07_scope_and_audit}

\begin{thebibliography}{9}

\bibitem{ConnesConsani2023}
A.~Connes and C.~Consani,
\emph{Spectral triples and \(\zeta\)-cycles},
Enseign. Math. \textbf{69} (2023), 93--148.
\href{https://doi.org/10.4171/LEM/1049}{doi:10.4171/LEM/1049}.

\bibitem{CCM2025}
A.~Connes, C.~Consani, and H.~Moscovici,
\emph{Zeta Spectral Triples},
arXiv:2511.22755 (2025).
\href{https://arxiv.org/abs/2511.22755}{arXiv:2511.22755}.

\bibitem{Conrey1989}
J.~B. Conrey,
\emph{More than two fifths of the zeros of the Riemann zeta function
are on the critical line},
J. Reine Angew. Math. \textbf{399} (1989), 1--26.
\href{https://doi.org/10.1515/crll.1989.399.1}
{doi:10.1515/crll.1989.399.1}.

\end{thebibliography}

\end{document}
